Gringo 2.0\\--Draft--

### 2008-09-04 doc/documentation/appendix.tex
fixed some spelling mistakes in gringo errors, DOKU: redesign, fixed appendix, added new warnings <- description still missing
git-svn-id: https://potassco.svn.sourceforge.net/svnroot/potassco/branches/gringo2@491 3e02f596-3131-0410-8352-e04eeaec37cc

IDENTIFIER      = [LETTER | UNDERSCORE], {IN_STRING};
STRING          = '"' {INSTRING-('"' | 'NL')} '"';
VARIABLE        = [CAP_LETTER],  {IN_STRING};
COMMENT         = '%' {IN_STRING-NL}, NL;
SHOW            = ['#'], 'show';
HIDE            = ['#'], 'hide';
CONST           = ['#'], 'const';
DOMAIN          = ['#'], 'domain';
MINIMIZE        = ['#'], 'minimize';
MAXIMIZE        = ['#'], 'maximize';
COMPUTE         = ['#'], 'compute';
DISJUNCTION     = '|';
LPARA           = '(';
RPARA           = ')';
LBRAC           = '{';
RBRAC           = '}';
LSBRAC          = '[';
RSBRAC          = ']';
DOT             = '.';
DOTS            = '..';
SEMI            = ';';
DDOT            = ':';
COMMA           = ',';
PLUS            = '+';
TILDE           = '~';
OR              = '?';
AND             = '&';
XOR             = '^';
MINUS           = '-';
TIMES           = '*';
DIVIDE          = '/';
ASSIGN          = '=';
EQ              = '==';
NE              = '!=';
GT              = '>';
LT              = '<';
GE              = '>=';
LE              = '<=';

@@

PROGRAM = PROGRAM, RULE, DOT;
PROGRAM = PROGRAM, SHOW, SHOW_LIST, DOT;
PROGRAM = PROGRAM, HIDE, HIDE_LIST, DOT;
PROGRAM = PROGRAM, DOMAIN, DOMAIN_LIST, DOT;
PROGRAM = PROGRAM, CONST, IDENTIFIER, ASSIGN, CONST_TERM, DOT;
PROGRAM = DOT;

>>>>

IDENTIFIER      = [LETTER | UNDERSCORE], {IN_STRING};
STRING          = '"', {INSTRING-('"' | 'NL')}, '"';
VARIABLE        = [CAP_LETTER],  {IN_STRING};
COMMENT         = '%', {IN_STRING-NL}, NL;
BLOCK_COMMENT   = '%*', {IN_STRING | NL}, '*%';
SHOW            = ['#'], 'show';
HIDE            = ['#'], 'hide';
CONST           = ['#'], 'const';
DOMAIN          = ['#'], 'domain';
MINIMIZE        = ['#'], 'minimize';
MAXIMIZE        = ['#'], 'maximize';
COMPUTE         = ['#'], 'compute';
BASE            = ['#'], 'base';
CUMULATIVE      = ['#'], 'cumulative';
VOLATILE        = ['#'], 'volatile';
DISJUNCTION     = '|';
LPARA           = '(';
RPARA           = ')';
LBRAC           = '{';
RBRAC           = '}';
LSBRAC          = '[';
RSBRAC          = ']';
DOT             = '.';
DOTS            = '..';
SEMI            = ';';
DDOT            = ':';
COMMA           = ',';
PLUS            = '+';
TILDE           = '~';
OR              = '?';
AND             = '&';
XOR             = '^';
MINUS           = '-';
TIMES           = '*';
DIVIDE          = '/';
ASSIGN          = '=';
EQ              = '==';
NE              = '!=';
GT              = '>';
LT              = '<';
GE              = '>=';
LE              = '<=';

@@

PROGRAM = PROGRAM, RULE, DOT;
PROGRAM = PROGRAM, SHOW, SHOW_LIST, DOT;
PROGRAM = PROGRAM, HIDE, HIDE_LIST, DOT;
PROGRAM = PROGRAM, DOMAIN, DOMAIN_LIST, DOT;
PROGRAM = PROGRAM, CONST, IDENTIFIER, ASSIGN, CONST_TERM, DOT;
PROGRAM = PROGRAM, BASE, DOT;
PROGRAM = PROGRAM, CUMULATIVE, IDENTIFIER, DOT;
PROGRAM = PROGRAM, VOLATILE, IDENTIFIER, DOT;
PROGRAM = DOT;
